Panel Seminars

### 2023-02-13 index.Rmd
minor change to index file to reference new section on contributions

The original MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics. *We are always looking for folks to join and write content for the website, if interested please [contact us](#contact)!*

@@

# Making contributions to the MarineOmics website
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).

>>>>

The original MarineOmics working group is part of the [RCN for Evolution in Changing Seas](https://rcn-ecs.github.io/), and was formed to promote **reproducible** and **robust** genomic research in nonmodel species, but especially marine and aquatic studies. Methods in next generation sequencing and bioinformatics advance at a pace that quickly render any static set of best practices obsolete. MarineOmics aims to support robust genomic research in ecology and evolution by disseminating guidelines through this dynamic, open-sourced website addressing introductory and advanced topics of population- and functional genomics. *We are always looking for folks to join and write content for the website, if interested please [contact us](#contact) and see the [below section](#contributions)!*

@@

# Making contributions to the MarineOmics website {#contributions}
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
